### 2020-05-30 writeup/experiments.tex
update table layout
re structure

\subsection{Improving training efficiency in MTL}

\subsection{Validating the Algorithmic Implications}

\textbf{A metric to determine positive or negative transfer.}
We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on STL results.
Table \ref{tab:mtl_better_than_stl} shows that using a threshold of $0.1$, we can predict $75.6\%$ among 150 task pairs for the sentiment analysis tasks with $38.8\%$ recall.
Similar for 91 image classification task pairs.
Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.

\begin{table}
	\centering
	\subfloat[Ablation study on when should use MTL via different source/target
	task accuracy.\label{tab:mtl_better_than_stl}]{%
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text
		classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\	
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}}
	\quad% --- set horizontal distance between tables here
	\subfloat[Taskonomy experiment.\label{tab:taskonomy}]{%
	\begin{tabular}{c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3}
		& {\bf Standard} & {\bf Alignment} \\
		\midrule
		{\bf MLP}  & > 100\% & 39\% \\
		{\bf LSTM} & 36\% & 36\% \\
		\bottomrule
		\end{tabular}}
\end{table}

@@

\textbf{MTL improves labeled data efficiency.}
We measure the data efficiency ratio on the sentiment analysis tasks.
We find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks.
If TREC is not included, we see that only $25\%$ of the labeled data is needed.

\textbf{Covariance alignment.}
We validate that the performance of aligning task covariances depends on the size of source task data.
In Figure \ref{fig_covariate}, we observe that the benefit from aligning task covariances becomes more significant as we increase the size of the source task dataset.

>>>>

\subsection{Experimental Results}

\textbf{A metric for the diagnosis of MTL.}
We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on STL results.
Table \ref{tab:mtl_better_than_stl} shows that using a threshold of $0.1$, we can predict $75.6\%$ among 150 task pairs for the sentiment analysis tasks with $38.8\%$ recall.
Similar for 91 image classification task pairs.
Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.

\textbf{Improving training efficiency via an incremental schedule.}
\todo{}

\subsection{Ablation Studies}

\textbf{Task similarity.} \todo{}

\begin{table}
\begin{minipage}[t]{.58\textwidth}
	\centering
  \begin{tabular}{c c c c c}
	\toprule
		\multirow{2}{*}{{\bf Threshold}}  & \multicolumn{2}{c}{{\bf Text
		classification}} & \multicolumn{2}{c}{{\bf ChestX-ray14}} \\
		& Precision &  Recall & Precision &  Recall \\
		\cmidrule(lr){1-1} \cmidrule(lr){2-3} \cmidrule(lr){4-5}
		0.0 & 0.596 & 1.000 & 0.593 & 1.000 \\
		0.1 & 0.756 & 0.388 & 0.738 & 0.462 \\
		0.2 & 0.919 & 0.065 & 0.875 & 0.044 \\	
		% 0.3 & 1.000 & 0.004 &     - &     - \\
	\bottomrule
	\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Ablation study on when should use MTL via different source/target task accuracy.}
	\label{tab:mtl_better_than_stl}
\end{minipage}
\quad
% \vspace{}
\begin{minipage}[t]{.40\textwidth}
	\centering
	\begin{tabular}{c c c}
		\toprule
		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
		MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} \\
		\cmidrule(lr){2-3}
		& {\bf Standard} & {\bf Alignment} \\
		\midrule
		{\bf MLP}  & > 100\% & 39\% \\
		{\bf LSTM} & 36\% & 36\% \\
		\bottomrule
		\end{tabular}
	\vspace{0.1in}
	\captionof{table}{Taskonomy experiment.}
	\label{tab:taskonomy}
\end{minipage}
\end{table}

@@

\textbf{Data size and efficiency.}
We measure the data efficiency ratio on the sentiment analysis tasks.
We find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks.
If TREC is not included, we see that only $25\%$ of the labeled data is needed.

\textbf{Covariate shift.}
We validate that the performance of aligning task covariances depends on the size of source task data.
In Figure \ref{fig_covariate}, we observe that the benefit from aligning task covariances becomes more significant as we increase the size of the source task dataset.

### 2020-05-30 writeup/transfer.tex
re structure

\subsection{Task Dissimilarity}\label{sec_similarity}

@@

\textbf{Algorithmic implication.}
We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
If $\sigma_1$ is too large, then the source task provides a negative transfer to the target.
If $\sigma_1$ is small, then the transfer may be positive.
Proposition \ref{prop_var_transition} formalizes the intuition.

@@

\subsection{Data Size}
In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the data sizes are equal for all tasks \cite{B00,M06,MPR16}.
More generally, such results are still applicable when all task data are being added simultaneously.
On the other hand, for many applications of multi-task learning, the data sources are usually heterogeneous.
For such settings, we have observed that adding more labeled data from one task does not always help.
%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
Using the isotropic model, we consider what happens if we vary the source task data size.

@@

\textbf{Algorithmic implication.}
We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
This is formalized as follows.

@@

@@

\textbf{Algorithmic implication.}
Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
When the source task data size is particularly large compared to the target task, then we expect that applying the covariance alignment algorithm results in a more significant gain.

>>>>

\subsection{Task Similarity}\label{sec_similarity}

@@

\textbf{Algorithmic consequence.}
We further show that multi-task learning is particular powerful when the labeled data of the source task is less noisy compared to the target task.
Consider a more general setting of Proposition \ref{prop_dist_transition} where the noise level $\sigma_1$ of task $1$ differs from the noise level $\sigma_2$ of task $2$.
If $\sigma_1$ is too large, then the source task provides a negative transfer to the target.
If $\sigma_1$ is small, then the transfer may be positive.
Proposition \ref{prop_var_transition} formalizes the intuition.

@@

\subsection{Data Size and Efficiency}
In classical Rademacher or VC based theory of multi-task learning, the generalization bounds are usually presented for settings where the data sizes are equal for all tasks \cite{B00,M06,MPR16}.
More generally, such results are still applicable when all task data are being added simultaneously.
On the other hand, for many applications of multi-task learning, the data sources are usually heterogeneous.
For such settings, we have observed that adding more labeled data from one task does not always help.
%On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
Using the isotropic model, we consider what happens if we vary the source task data size.

@@

We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
This is formalized as follows.

@@

\textbf{Algorithmic consequence.} \todo{}

@@

\textbf{Algorithmic consequence.}
Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
When the source task data size is particularly large compared to the target task, then we expect that applying the covariance alignment algorithm results in a more significant gain.
